A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Cut for space, we do better later anyway
ie

Next, extend the mapping by pairing a vertex in $G$ with a vertex in $H$ of the
same label; we will choose to map vertex $2$ to vertex $d$, giving $M=\{1a,
2d\}$ (\cref{fig:alg3}).  Each unmapped vertex $v \in \V(G)$ is labelled
with a two-character bit string, indicating its adjacency to each of
the two mapped vertices in $\V(G)$ (vertices $1$ and $2$).  For example, vertex
$3$ is labelled $01$, indicating that it is not adjacent to vertex $1$ but is adjacent
to vertex $2$.  Labels are given to unmapped vertices in $\V(H)$ in a similar fashion,
showing adjacency to matched vertices $a$ and $d$.

Our invariant is maintained: we can extend $M$ by a vertex pairing if and only
if the two vertices have the same label. Note also that the labels can be
calculated efficiently, since each label (in \cref{fig:alg3}) is prefixed
by the label at the previous level of the search tree (\cref{fig:alg2}).

@@

The algorithm backtracks when the incumbent, i.e. the largest matching found so far, is at least as large
as a calculated bound given $M$ and the current labelling. To demonstrate how
this bound is calculated, we consider the situation one level deeper in the
search tree shown in \cref{fig:alg4}.

@@

Where CP-FC uses a soft allDifferent constraint to filter and compute a bound,
\McSplit\ computes a bound from each label class in the future, i.e. it
performs Hall Set reasoning on the fly.

@@

We have yet to fully investigate variable and value ordering heuristics, i.e. the selection of a label class and the selection of a vertex from that label class.
There is also the potential to branch on both sides, that is instead of branching on vertices in $\V(G)$, it would be equally valid to branch on
a vertex in $\V(H)$ , since our data structure treats the
two graphs symmetrically. More interestingly, we could choose which graph to branch on
at each search node using some heuristic (perhaps choosing based on whether the $P$ or
$T$ set is smaller), so long as we can ensure that the search remains complete.

>>>>

Next, extend the mapping by pairing a vertex in $G$ with a vertex in $H$ of the
same label; we will choose to map vertex $2$ to vertex $d$, giving $M=\{1a,
2d\}$ (\cref{fig:alg3}).  Each unmapped vertex $v \in \V(G)$ is labelled
with a two-character bit string, indicating its adjacency to each of
the two mapped vertices in $\V(G)$ (vertices $1$ and $2$).  For example, vertex
$3$ is labelled $01$, indicating that it is not adjacent to vertex $1$ but is adjacent
to vertex $2$.  Labels are given to unmapped vertices in $\V(H)$ in a similar fashion,
showing adjacency to matched vertices $a$ and $d$.  Our invariant is
maintained: we can extend $M$ by a vertex pairing if and only if the two
vertices have the same label.

@@

The algorithm backtracks when the incumbent (the largest matching found so far) is at least as large
as a calculated bound given $M$ and the current labelling. To demonstrate how
this bound is calculated, we consider the situation one level deeper in the
search tree shown in \cref{fig:alg4}.

@@

Where CP-FC uses a soft allDifferent constraint to filter and compute a bound,
\McSplit\ computes a bound from each label class in the future, i.e.\ it
performs Hall Set reasoning on the fly.

@@

We have yet to fully investigate variable and value ordering heuristics, i.e.\ the selection of a label class and the selection of a vertex from that label class.
There is also the potential to branch on both sides, that is instead of branching on vertices in $\V(G)$, it would be equally valid to branch on
a vertex in $\V(H)$ , since our data structure treats the
two graphs symmetrically. More interestingly, we could choose which graph to branch on
at each search node using some heuristic (perhaps choosing based on whether the $P$ or
$T$ set is smaller), so long as we can ensure that the search remains complete.
